ad_ques12.2

### 2022-10-19 hw8-1/ashish_ques12.2.Rmd
completed ques12.2

```{r}
factorial_doe = FrF2(nruns = n_combinations,nfactors =  n_variables)
factorial_doe
```

@@

>>>>

```{r}
factorial_doe = FrF2(nruns = n_combinations,nfactors =  n_variables,
                     default.levels = c(0,1))
factorial_doe
```

Note here 1 means binary variable present, and 0 means otherwise

```{r}
summary(factorial_doe)
```

The #generators =10-4 = 6. B'cos 16 = 2\^4.

@@

### Feature distribution

```{r}
factorial_doe1 = as.data.frame(factorial_doe)
```

```{r}
factorial_doe1$sum = as.numeric(factorial_doe1$A)+as.numeric(factorial_doe1$B)+as.numeric(factorial_doe1$C)+as.numeric(factorial_doe1$D)+as.numeric(factorial_doe1$E)+as.numeric(factorial_doe1$F)+as.numeric(factorial_doe1$G)+as.numeric(factorial_doe1$H)+as.numeric(factorial_doe1$J)+as.numeric(factorial_doe1$K)-10
table(factorial_doe1$sum)
```
